An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-05 scagnostics.Rmd
Considerations on holes index.

>>>>

((Notes on holes/cmass indices)):

Holes index in $d=2$ dimensional projections, we have projected data given by 
\begin{equation}
m = \begin{pmatrix}
x_1 & y_1 \\
x_2 & y_2 \\
\vdots & \vdots \\
x_n & y_n
\end{pmatrix}
\end{equation}
In tourr calculate holes index as $num/den$ where for $d=2$ we have
\begin{equation}
num = 1 - \frac{1}{n} \sum_{i=1}^n e^{(x_i^2+y_i^2)/2}
\end{equation}
and $den$ is fixed for fixed number of dimensions, here $den = 1 - \frac{1}{e}$. Considering now the case where all $x_i, y_i \leq 1$ we can see that points at the edge may lead to larger values than points on a circle, $x_i^2+y_i^2 = 1$. Note also that we cannot give generic upper limit on the index values, it will depend on the range, in particular values $>1$ also possible. Cmass calculated as $1-holes$, will take negative values if $holes>1$, e.g. the case for entries $x_i, y_i > 1$, example:

```{r sillyExample, echo=TRUE}

mX <- matrix(c(2,2,2,2), nrow=2)
holes(mX)
cmass(mX)
# compare random points on circle to extreme positions
mC <- matrix(c(cos(1.2*pi), sin(1.2*pi), cos(pi/3), sin(pi/3), cos(0.6*pi), sin(0.6*pi)), ncol = 2)
mT <- matrix(c(1,0,0,1,1,1), ncol=2)
holes(mC)
holes(mT)
```
